\documentclass[dvipdfmx,a4paper]{article}
\usepackage{color,a4wide}
\usepackage[dvipdfmx]{hyperref}

\setlength{\oddsidemargin}{-1.8truecm}
\setlength{\textwidth}{19.6truecm}
\setlength{\headsep}{0truecm}
\setlength{\topmargin}{-2truecm}
\setlength{\textheight}{27truecm}
\pagestyle{empty}

\def\hyperlink#1#2{\href{#1}{\color{blue}\underline{#2}\color{black}}}
\sloppy

\begin{document}

\section*{Kentaro Hara \textmd{\normalsize{(Contact: xharaken@gmail.com, +81-080-8429-1712, Tokyo Japan)}}}

\subsubsection*{\;Skills}
\vskip-0.4em\hrule\vskip1em

\begin{itemize}
\item Tech-leading large-scale engineering projects across globally distributed offices.
\item Deep technical expertise on large-scale software design and implementation, including open source platform development.
\item Building a strong organization of engineers with diverse backgrounds.
\item Building partnership with universities and teaching computer science to underrepresented students to increase diversity in the tech industry.
\item Deep expertise on economic theories and blockchain technologies.
\item Programming languages: C/C++, Python, JavaScript, Java
\item Technologies: Open source platforms, Web platforms, Browser engines, Operating systems, Programming language runtime, Garbage collections, Memory allocators, Parallel and distributed programming, Performance optimization, Cryptocurrencies, Blockchains
\item Speaking languages: English (full professional proficiency, TOEIC 965), Japanese (native)
\end{itemize}

\subsubsection*{\;Work experience}
\vskip-0.4em\hrule\vskip1em

\quad\textbf{Google, Tokyo, Japan}\par
\quad\textbf{Principal Software Engineer} (2021 | Present; the most promoted position as a software engineer in Google Japan)\par
\quad\textbf{Senior Staff Software Engineer} (2017 | 2021)\par
\quad\textbf{Staff Software Engineer} (2014 | 2017)\par
\quad\textbf{Senior Software Engineer} (2013 | 2014)\par
\quad\textbf{Software Engineer} (2011 | 2013)\par

\begin{itemize}
\item Worked as the most active reviewer of Chromium and reviewed 22000 patches from 600+ engineers. Worked as a top-level owner of Chromium and made various key engineering decisions that affect the entire codebase.
\item Worked as a technical lead of Chromium's rendering engine architecture. Led multiple large-scale projects across distributed offices in London, Munich, Paris, Sydney, San Francisco, Waterloo etc. Designed and implemented large-scale foundational systems of the browser engine, including a C++ garbage collection, massive memory reductions, security primitives to improve memory safety, browser's back-forward cache and large-scale code refactoring. Some of the design documents are published \hyperlink{https://haraken.info/index.php?tag=reajklff}{here}.
\item Worked as a people manager for a Chrome Browser Tokyo team (40 engineers). Established a high-performing organization by investing in diversity, inclusion, trust and psychological safety.
\item To increase diversity in the tech industry, launched \hyperlink{https://www.youtube.com/watch?v=-5v5sTUXtkk}{STEP} as an education program for underrepresented students in Japan (300+ students graduated in the past 9 years with my direct contributions). Organized 20+ university workshops to inspire students. Worked as an engineering lead of Google Japan's internship program and strategically designed the program structure that converted many interns to full-time employees, realizing their dreams.
\item Patents: GP-18781-00-US, GP-18511-00-US, GP-13193-00-US
\end{itemize}

\subsubsection*{\;Education}
\vskip-0.4em\hrule\vskip1em

\quad\textbf{The University of Tokyo}\par
\quad\textbf{Master's degree, Information Science and Technology} (2009 - 2011)\par
\quad\textbf{Bachelor's degree, Faculty of Engineering} (2005 - 2009)\par

\begin{itemize}
\item Researched parallel and distributed programming languages. Full publications are available \hyperlink{https://haraken.info/index.php?tag=o2jfanvk}{here}.
\item Got the award from the Chairman of Faculty of Engineering of the University of Tokyo (東京大学工学部長賞) for \hyperlink{https://haraken.info/index.php?tag=btpwdr22}{my graduate thesis}.
\item Got the award from the Chairman of Graduate School of Information Science and Technology of the University of Tokyo (東京大学情報理工学系研究科長賞) for \hyperlink{https://haraken.info/index.php?tag=oiureqll}{my master thesis}.
\end{itemize}

\subsubsection*{\;Hobby projects}
\vskip-0.4em\hrule\vskip1em

\begin{itemize}
\item Have deep expertise on economic theories. Ranked 2nd in the employment examination of Japan's National Public Servants for economics (国家公務員総合職 経済).
\item Passionate about blockchain technologies and launched an algorithm-based stablecoin called \hyperlink{https://github.com/xharaken/john-law-coin}{JohnLawCoin}.
\end{itemize}

\end{document}
